---
title: "Experiment materials"
output:
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(osfr)
```

Last update: `r Sys.Date()`

# Overview

This directory contains the files used for the norming study and for the production experiment:

- The `norming/` directory hosts the images of the objects with modified color used in the norming study and the results (ratings) of the study.
- The `experiment/` directory contains the randomization lists for each participant in the production study.


```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Data")
```

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "exp-materials") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

