---
title: "Norming study"
output:
  github_document:
    html_preview: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)
library(osfr)
```

Last update: `r Sys.Date()`

# Overview

This directory contains the files of the norming study, designed to obtain typicality ratings of re-colored images of everyday objects.

There are 2 subdirectories:

- The `images/` directory contains the re-colored images used in the norming study.
- The `results/` directory holds an aggregated `tipicality.csv` file with the typicality ratings of each image/object for each participant.

The `tipicality.csv` file has the following columns:

- `prolific id`: The participant/trial id.
- `object`: The name of the object represented in the image.
- `typicality`: The typicality rating (numeric, `1-100`, `1` = most atypical, `100` = most typical).
- `colour`: The color of the object in the image.

```{r retrieve}
# Main repo "Many Speech Analysis": https://osf.io/3bmcp/
osf_repo <- osf_retrieve_node("3bmcp")
# Repo components
osf_comps <- osf_ls_nodes(osf_repo)
# Dataset & Materials component
data_comp <- osf_comps %>% filter(name == "Data")
```

```{r data_files, include=TRUE}
osf_ls_files(data_comp, "norming") %>%
  select(name) %>%
  filter(str_detect(name, ".*\\.md", negate = TRUE)) %>%
  arrange(name)
```

